Supporting Information

### 2018-04-17 SupportingInformation.Rmd
results for BMR data sets added

fractxt<-function(fracval,numsurrog=1000){
  ptxt<-''
  if (fracval>.5*numsurrog){                        # why 0.5 factor?
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog){
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}

@@

 #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$","$\\Ps_{0,0.1}-\\Ps_{0.9,1}$","$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 atdres<-data.frame(Statistic=c("$\\cor_{first.slice}-\\cor_{last.slice}$",
                                "$\\Ps_{first.slice}-\\Ps_{last.slice}$",
                                "$\\Dsq_{first.slice}-\\Dsq_{last.slice}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

@@

```{r read_plot_BMR_data, echo=FALSE, results="hide"}
set.seed(seed=101)
source("phylo_dat_fn.R")
#---------------------------------------------------------
BMR_dat<-read.csv("./Data/BMR/bmr-contrasts.csv",header = T)
#class(BMR_dat)
v_BMR<-phylo_dat_fn(data=BMR_dat,i=4,j=3,ploton = F)

pdf("./Results/BMR_results/BMR_vs_lnmass.pdf")
plot(v_BMR[,1],v_BMR[,2],col="blue",xlab="ln(mass)",ylab="BMR") # copula plot btw ln(Mass) vs. BMR
dev.off()
```

@@

@@

```{r }
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
knitr::kable(tab_BMR_asym)
```

@@

>>>>

fractxt<-function(fracval,numsurrog=1000){
  ptxt<-''
  if (fracval>.5*numsurrog){                        # ?DCR why 0.5 factor?
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog){
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}

@@

 atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$",
                                "$\\Ps_{0,0.1}-\\Ps_{0.9,1}$",
                                "$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
 #atdres<-data.frame(Statistic=c("$\\cor_{first.slice}-\\cor_{last.slice}$",
 #                              "$\\Ps_{first.slice}-\\Ps_{last.slice}$",
 #                               "$\\Dsq_{first.slice}-\\Dsq_{last.slice}$"),
                   Kendall=rep("",3),
                   Spearman=rep("",3),stringsAsFactors = F)

@@

```{r read_plot_BMR_data, echo=FALSE, results="hide"}
set.seed(seed)
source("phylo_dat_fn.R")
#---------------------------------------------------------
BMR_dat<-read.csv("./Data/BMR/bmr-contrasts.csv",header = T)
#class(BMR_dat)
v_BMR<-phylo_dat_fn(data=BMR_dat,i=4,j=3,ploton = F)

pdf("./Results/BMR_results/BMR_vs_lnmass.pdf")
op<-par(mar=c(5,5,5,5))
plot(v_BMR[,1],v_BMR[,2],col="red",xlab="ln(mass)",ylab="BMR",cex.lab=2,cex.axis=2) # copula plot btw ln(Mass) vs. BMR
par(op)
dev.off()
```

![Copula plot for BMR dataset \label{fig_BMR_cop}](./Results/BMR_results/BMR_vs_lnmass.pdf){ width=30%, height=30% }

@@

<!--Display model selection results for BMR data in a table-->
```{r tab_BMRfit, echo=F, results='markup'}
h<-BivMS_BMR$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for BMR dataset. \\label{tab_BMRfit}",
             booktabs=T)
```

@@

![Nonparametric tests for tail dependence and other deviations from a normal copula for BMR data. As described in Methods, each statistic was computed on the data using the ranges $0-0.1$, $0.1-0.2$, ..., $0.9-1$ (red lines), and was also computed using the same ranges for 1000 normal-copula surrogate datasets (dashed lines show 0.025 and 0.975 quantiles of these results and dotted lines show 0.005 and 0.995 quantiles). \label{fig_BMR_nonparam}](./Results/BMR_results/BMR_bivfunctionplot.pdf)

```{r tab_BMR_asym, echo=F, results="markup"}
tab_BMR_asym<-make_table_stat_fn(data=stat_BMR_ga)
knitr::kable(tab_BMR_asym,
             format="pandoc",
             caption = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis (best fit is here Frank with symmetric tail dep)? \\label{tab_BMR_asym}",
             booktabs=T)
```

@@

![Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_params_GOF}](./Results/Cause4copula_results/compare_params_pGOF.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Clayton** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_C_spear}](./Results/Cause4copula_results/Clayton_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Clayton** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_C_kend}](./Results/Cause4copula_results/Clayton_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Clayton** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SC_spear}](./Results/Cause4copula_results/SClayton_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Clayton** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SC_kend}](./Results/Cause4copula_results/SClayton_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Gumbel** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_G_spear}](./Results/Cause4copula_results/Gumbel_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Gumbel** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_G_kend}](./Results/Cause4copula_results/Gumbel_kendall.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Gumbel** copula and of the affected populations for 9 equidistant **Spearman's Rho** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SG_spear}](./Results/Cause4copula_results/SGumbel_spearman.pdf)

![Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from **Survival Gumbel** copula and of the affected populations for 9 equidistant **Kendall's Tau** values in a range (0.1 to 0.9) (Initially 5000 points are generated but we kept last 500 points for both noise and population data for comparison) \label{fig_Cause4copula_SG_kend}](./Results/Cause4copula_results/SGumbel_kendall.pdf)
